Real-time resolving assembly graph by ONT long reads data

### 2019-11-18 paper.tex
conclusion

%Set abstract (see below)
\abstract{
A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either saving sequencing resources or reducing turnaround time for data analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods. 
Here we present \npgraph{}, a real-time hybrid assembly software using the assembly graph instead of the separated pre-assembly contigs. It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide. 
The applications on synthetic and real data set of isolate genomes show improved accuracy while still maintain the required computational cost at very low level. In addition, the GUI feature can provide users a comprehensive look-and-feel of the whole assembly process. The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
%=======
%A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies. Here we present another real-time hybrid assembler, \npgraph{}, that can work on the assembly graph instead of the pre-assembled contigs. The results show improved accuracy while still minimize the required computational cost. The tool is available at \url{https://github.com/hsnguyen/assembly}.
%>>>>>>> 2d4c481dd93902dfb2dabe46534a62e8a8c2058c
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
% \begin{itemize}
% \item The importance of having a real-time assembler for bacterial and small genomes: e.g. npscarf 
% \item The difficulty to resolve assembly graph in real-time.
% \item Available hybrid assembly methods using long reads: unicycler, ...
% \item an online algorithm to resolve assembly graph by long reads is needed, ...
% \item Requirements
%     \begin{itemize}
%     \item Support streaming: efficient with high yield (armortized analysis)
%     \item Statistically robust: online modification of the dynamic graph, back tracking edge deletion...
%     \item Standardisation : output GFA in real-time
%     \end{itemize}
% \end{itemize}
Streaming assembly methods have been proven to be useful in saving time and resources compared to the traditional batch algorithms with examples included \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}. The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed. This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a DBG construction while waiting for the data being retrieved.

\npscarf{}, on the other hand, works on the available short-read assembly to scaffold the contigs using nanopore sequencing which is well-known by the real-time property. The completion of genome assembly along with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.  
However, due to the greedy approach of a streaming algorithm, as well as being an alignment-based-only scaffolding mechanism, running the tool with default settings suffers from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. In many case, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well. 
To tackle the quality issue while maintaining its streaming execution, an assembly graph processing system is investigated as it would provide an additional high-quality source of linking information for the assembly operations.

After the construction of an assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.
Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} or \unicycler{} \cite{Wick2017unicycler}. 
In general, the available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
In which, the \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with mininum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are attained. In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
While the later approach employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal. For that reason, the first direction is more suitable for a real-time pipeline.

However, the challenges to adapt this approach into a real-time mechanism are obvious and mainly come from the heavy path-finding task and the complication of self-improvement step which is critical to a streaming algorithm. 
A modified DFS algorithm and a voting system with accumulating scores calculation has been implemented to overcome these issues.
This results in \npgraph{}, an user-friendly tool with GUI that can traverse the assembly graph and scaffold its components in real-time as long as the nanopore sequencing process is running and continuously generating long reads.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\subsection*{\npgraph{} -- a tool to resolve assembly graph in real-time}
\npgraph{}'s input consists of Illumina assembly graph resulted from running assembler, e.g. \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$ \cite{Zerbino2008}, $\mathtt{AbySS}$ \cite{Simpson2009} on Illumina short reads, together with long reads from third generation sequencing technology (Oxford Nanopore Technology, Pacbio).
The long reads will be aligned with the contigs in the assembly graph to indicate longer paths that should be traversed. These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
\npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.

@@

\subsection*{Hybrid assembly for synthetic data sets}
To evaluate the performance of the method, \npgraph{} was benchmarked against \spades{} with its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{} with/without assembly graph integrated, and Unicycler version 0.4.6 on the latter's testing data~ \cite{Wick2017unicycler} . This data set were simulations of Illumina and MinION raw data, generated \emph{in silico} based on random and available microbial references. 
Specifically, the synthetic Illumina data was generated by using a wrapper script of ART~\cite{HuangLMM2012} that allows uniform coverage for circular genome sequencing with justifiable depths.
PBSIM~\cite{OnoAH2012}, on the other hand, was used to simulate the long reads.

There were three settings for each of the synthetic raw data (\emph{good, medium, bad}) corresponding to the quality, yield and length of reads being generated. 
In the SGS simulation, the \emph{bad} data consist of 100bp paired-end reads with low and uneven coverage (40X) leading to many dead ends in the assembly graph due to missing regions in the genome. 
The read length was 125bp in the \emph{medium} setting with better depth distributions that could cover the genome better. 
Finally, the \emph{good} option provided best data sets with 150bp of read length and 100X coverage.
While the quality of SGS reads would determine the assembly graph nature, the nanopore data plays critical role in graph resolving.
The three settings leveled up the depth (8X, 16X, 32X) and at the same time, average length ($5$Kbp, $10$Kbp, $20$Kbp) and maximum identities (90\% ,95\% ,98\%) respectively.
We only considered the \emph{good} configurations of both platforms for the sequence data being tested.
Also, since the other comparative tools do not support streaming assembly, there were only batch-mode runs being carried out and the reciprocal results were examined by QUAST 5.0.2~\cite{Mikheenko2018quast5}.

@@

Table~\ref{table:npgraph_compare} shows evaluation results for 5 synthetic data sets, the output of the full run can be found in Supplementary Table~\ref{supp_tab:synthetic_benchmark}.
In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the original scaffolder \npscarf{} was included as well as \npscarfg{} -- its modified version with assembly graph integrated.
On the other hand, \npgraph{} can use 2 different aligners, \bwa{} and \minimap{}, for its bridging phase thus both practices were included in this comparison.

In general, the graph integrated version of \npscarf{} improved the assembly results in terms of mis-assemblies and error reduction while virtually consuming similar resources compared to the original version.
The only exception where the number of mis-assemblies being increased was the simulation of a random sequence with many repeats. There were 10 more mistakes detected using the later version \npscarfg{}. However, with additional investigations, we found that the number of mis-assemblies on the true positive circular sequences (3 from the reference) has been significant reduced by applying assembly graph for \npscarf{}. The errors mostly came from redundant sequences output from the software due to the failure in estimation of contig multiplicity.
Even though using assembly graph for gap fillings, there were no changes in the way to determine if a contig is unique or not from \npscarfg{}. 
It still relied on the length and coverage statistics, \IE{} \emph{Astats}~\cite{MyersSD2000} to find anchors that were critical for the backbone construction of the assembly.
Redundant path findings for false positive replicons consequently returned additional wrong translocations in the final contigs which were reported by QUAST. 
Other than that, the method had successfully produced better assemblies than the original. Regarding \emph{Mycobacterium tuberculosis} H37Rv, the number of mis-assembled breakpoints had been trimmed down from 12 to 2, while the number of final contigs had reduced from 4 to only one as in the reference. Results in cases of \ec{} O25b H4ST131 and \emph{Streptococcus suis} BM407 also showed enhancements in terms of those categories as well as N50 statistics. 
There was improvements considering the nucleotide errors (mismatches and indels) as well from aforementioned data sets, except for the \ec{} when slightly more mismatches had been detected. However, these errors can be corrected by running polishing tools with the raw Illumina data afterward.

@@

To align the long reads to the assembly graph components, either \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} was invoked in \npgraph{}. 
The former option was inherited from \npscarf{} pipeline with the intact parameters
%$-k11 -W20 -r10 -A1 -B1 -O1 -E1 -L0 -a -Y$
while the latter was used with the recommended settings (-$\mathtt{k}$15 -$\mathtt{w}$5) for the best sensitivity working on MinION data.
Even though, \bwa{} normally reported more hits than \minimap{} but at the same time, was responsible for more false positive alignments.
For instance, regarding the last data set from Table~\ref{table:npgraph_compare}, the assembly of \npgraph{} using \bwa{} was suffered from the ambiguous alignments thus more fragmented than the other counterparts. 
On the other hand, referring to more complicated graphs from \emph{Acinetobacter} A1 and the yeast \emph{Saccharomyces cerevisiae} S288c from Table~\ref{supp_tab:synthetic_benchmark}, the number of mis-assemblies from using \minimap{} were increased due to the lacks of appropriate alignments to support accurate bridging process.
However, under almost circumstances, using either aligners would result in final assemblies with similar qualities.
Furthermore, in terms of running time and resources required, \minimap{} proved to be the best option. 
The total CPU hours had been trimmed down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
This feature is certainly more favoured to a real-time assembly as well.
As the consequence, as long as \minimap{} is expected to replace \bwa{} for long-read sequencing data alignment, it would likewise become the main aligner for \npgraph{} pipeline in the future.

It is noteworthy to discuss in more details the errors addressed in the above assembly methods.
This figure measured the total mismatches and indels per 100kpb from the assembly sequences when mapping to the reference.
As expected from hybrid assemblies where Illumina sequencing data were used as the main building blocks, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) for almost every case.
In addition, the indels errors, which mainly caused by TGS data, were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
The majority of the differences accounted for the mismatched nucleotides caused by the alternative paths connecting the unique anchors from the backbone of the assembly.
This phenomenon may root from homologous repeats or sequencing errors of the genome.
From all the hybrid assemblers, $\mathtt{hybridSPAdes}$ reported results with highest fidelity. This meant that the performance its decision-rule algorithm $\mathtt{exSPAnder}$~\cite{Prjibelski2014} was the most accurate amongst all path finding methods. As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies in cases of \emph{Streptococcus suis} or \emph{Acinetobacter} samples (Table~\ref{table:npgraph_compare} and \ref{supp_tab:synthetic_benchmark}).
\unicycler{}, which employs an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads, returned the second best reliable and at the same time, closest-to-complete results overall.
\npscarf{}, on the other hand, exploited the long reads for the gap filling thus inherited the high error rates from them.
By integrating the assembly graph for the task, the errors were reduced in general (random sequences, \emph{M.~tuberculosis}, \emph{S.suis} from Table~\ref{table:npgraph_compare}) but not completely since the mis-placed contigs were still not resolved in other circumstances.
\npgraph{} significantly reduced the errors compared to \npscarf{}, however the figures were still higher than the those of the best counterparts.
This implied a more robust decision making system is needed in \npgraph{}'s real-time path finding module for even better output's accuracy.

\subsection*{Hybrid assembly for real data sets}
Several sequencing data sets of actual bacterial samples~\cite{George2017M14} were used in this scenario.
The data included both Illumina paired-end and MinION sequencing based-call data for each sample.
Unlike previous settings, rather than the default output, the optimal \spades{} assembly graph detected by \unicycler{} were used for \npgraph{} algorithm as well.
This step had been proved to be useful in selecting the best graph available, amongst \spades{} runs with ranging $k$-mer values, that have dead-ends and number of contigs minimized~\cite{Wick2017unicycler}. Likewise, as mentioned before, the quality of the initial assembly graph would considerably influence the final results of \npgraph{}.

Due to the lack of available reference genomes, fewer statistics were reported by QUAST for the comparison of the results. 
Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies.
Table~\ref{tab:npgraph_real} shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.

@@

The assembly task for \emph{Enterobacter~cloacae} was more challenging as the chromosomal DNA sequence was not been fully resolved using either method. 
The chromosome size was estimated to be approximately $4.8$Mbp but had been broken into two smaller pieces. 
\npgraph{} returned longer stretches of length $3.324$Mbp and $1.534$Mbp while the figures were $2.829$Mbp and $1.978$Mbp from \unicycler{}'s output.
However, the number of circular sequences detected by \unicycler{} was one more than the other ($2$ versus $1$). They were corresponding to 2 plasmids, namely IncR and repA.
While the latter were recognized by both methods, the longer plasmid sequence was fragmented running \npgraph{}.
Similar to the previous data set, there were around $14$Kpb of data were unable to be finished by the assemblers.

@@

\subsection*{Real-time mode hybrid assembly}
Figure~\ref{F:npgraph_rt} demonstrates the real-time mode performance of \npscarf{} and \npgraph{} via N50 statistics during the assembly of 4 example data sets.
This experiment would discover the rate of completing genome assemblies of the new method, set aside the accuracy aspect which had already been discussed previously.
\npscarfg{} basically scaffolds the pre-assembly contigs in the same manner with the original version thus was not discussed here.

@@

\subsection*{Metagenomics assembly}
We further employed \npgraph{} on mock community data to study the performance of our method in metagenomics co-assembly problem.
In this application, sequencing data (including both short and long reads) from mixtures of ten microbial species of ZymoBIOMICS Microbial Community Standards \cite{Nick2019zymo} were used as input for \npgraph{}. 
The total genome size was estimated as 61.96 Mbp.
There were two settings for the input depending on the distribution of cell abundances in the mixture itself, namely even and log population.
On the other hand, 8 out of 10 genomes being sequenced were reconstructed by using PacBio sequencing (RSII and Sequel) previously \cite{Mcintyre2019zymo}, including \emph{Bacillus~subtills}, \emph{Enterococcus~faecalis}, \emph{Escherichia~coli}, \emph{Listeria~monocytogenes}, \emph{Pseudomonas~aeruginosa}, \emph{Saccharomyces~cerevisiae}, \emph{Salmonella~enterica} and \emph{Staphylococcus~aureus}. We evaluated the coassembly results by running $\mathtt{metaQUAST}$ given 8 PacBio assembly as references.

\begin{table}[!hpt]
\begin{center}
\caption{NGA50 improvement from $\mathtt{metaSPAdes}$ to \npgraph{} assembly on two mock communities ZymoLog and ZymoEven. The statistics were generated by $\mathtt{metaQUAST}$ v3.2 with 8 (out of 10) available PacBio references of individual isolates \cite{Nick2019zymo}.}
\label{table:zymo}
\begin{tabular}{|l|r|r|r|r|}
\hline
\multirow{2}{*}{\textbf{Community}} & \multicolumn{2}{|c|}{\textbf{ZymoEven}} & \multicolumn{2}{|c|}{\textbf{ZymoLog}} \\ \cline{2-5}
& $\mathtt{metaSPAdes}$ & \npgraph{} & $\mathtt{metaSPAdes}$ & \npgraph{} \\ \hline
\emph{B.~subtilis} & $23,386$ & $382,368$ & $35,390$ & $433,078$ \\ \hline
\emph{E.~coli} & $34,776$ & $1,108,989$ & $-$ & $-$ \\ \hline
\emph{E.~faecalis} & $23,340$ & $217,908$ & $-$ & $-$ \\ \hline
\emph{L.~monocytogenes} & $26,480$ & $520,012$ & $23,146$ & $130,284$ \\ \hline
\emph{P.~aeruginosa} & $59,372$ & $1,753,658$ & $161,816$ & $444,495$ \\ \hline
\emph{S.~aureus} & $26,058$ & $175,908$ & $-$ &$-$ \\ \hline
\emph{S.~cerevisiae} & $-$ & $-$ & $-$ & $-$ \\ \hline
\emph{S.~enterica} & $33,363$ & $4,242,458$ & $-$ & $-$ \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

%Set abstract (see below)
\abstract{
A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either saving sequencing resources or reducing turnaround time for data analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods. 
Here we present \npgraph{}, a real-time hybrid assembly software using the assembly graph instead of the separated pre-assembly contigs. It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide. 
The applications on synthetic and real data set of isolate genomes show improved accuracy while still maintain the required computational cost at very low level. In addition, the built-in graphical user interface (GUI) can provide users a comprehensive look-and-feel of the whole assembly process. The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
%=======
%A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies. Here we present another real-time hybrid assembler, \npgraph{}, that can work on the assembly graph instead of the pre-assembled contigs. The results show improved accuracy while still minimize the required computational cost. The tool is available at \url{https://github.com/hsnguyen/assembly}.
%>>>>>>> 2d4c481dd93902dfb2dabe46534a62e8a8c2058c
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
% \begin{itemize}
% \item The importance of having a real-time assembler for bacterial and small genomes: e.g. npscarf 
% \item The difficulty to resolve assembly graph in real-time.
% \item Available hybrid assembly methods using long reads: unicycler, ...
% \item an online algorithm to resolve assembly graph by long reads is needed, ...
% \item Requirements
%     \begin{itemize}
%     \item Support streaming: efficient with high yield (armortized analysis)
%     \item Statistically robust: online modification of the dynamic graph, back tracking edge deletion...
%     \item Standardisation : output GFA in real-time
%     \end{itemize}
% \end{itemize}
Streaming assembly methods had been proven to be useful in saving time and resources compared to the conventional batch algorithms with examples included \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}. The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed. This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a De Bruijn graph (DBG) construction while waiting for the data being retrieved.
\npscarf{}, on the other hand, is a hybrid assembler working on a pre-assembly set of short-read assembly contigs. It functions by scaffolding the contigs using nanopore sequencing which is well-known by the real-time property. The completion of genome assembly in parallel with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.

% Why hybrid???
Hybrd approaches are still common practice in genome assembly and data analyses when Illumina sequencing remains the most favoured option in terms of cost and accuracy to date.
On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the former`s assembly.
As the consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and comptete genomes at the same time.
\npscarf{}, following that philosophy, had been developed and deployed on real microbial genomes.

However, due to the greedy bridging approach of the contigs-based streaming algorithm, \npscarf{}`s concurrent results might suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
A default setting were optimzed for microbial genomes input but cannot fit for all data from various experiments in practice.
Also, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well. 
To tackle the quality issue while maintaining its streaming execution, a bridging method by assembly graph traversing is proposed. 
In which, after the construction of a compact DBG assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.

Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} or \unicycler{} \cite{Wick2017unicycler}. 
In general, the available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
In which, the \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with mininum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are attained. In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
While the latter method employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal. For that reason, the first direction is more suitable for a real-time pipeline.

Nonetheless, the challenges to adapt this approach into a real-time mechanism are obvious, mainly from building a progressive, self-updating path-finding and graph reducing method which are required for a streaming assembler on graph. 
A modified DFS (depth-first search) algorithm and a voting system with comprehensive scoringn system has been implemented to overcome these issues.
This results in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\subsection*{\npgraph{} -- a tool to resolve assembly graph in real-time}
\npgraph{}'s input consists of Illumina assembly graph resulted from running assembler, e.g. \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$ \cite{Zerbino2008}, $\mathtt{AbySS}$ \cite{Simpson2009} on Illumina short reads, together with long reads from third generation sequencing technology (Oxford Nanopore Technology, Pacbio).
The long reads will be aligned with the contigs in the assembly graph to indicate longer paths that should be traversed. These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
\npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.

@@

\subsection*{Evaluation using synthetic data}
To evaluate the performance of the method, \npgraph{} was tested against \spades{} with its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{} with/without assembly graph integrated, and Unicycler version 0.4.6 on Unicycler`s synthetic data set~ \cite{Wick2017unicycler} . The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on random and available microbial references. 
We ran all hybrid assembly methods in batch-mode and the reciprocal results were examined by QUAST 5.0.2~\cite{Mikheenko2018quast5}.

@@

Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, the output of the full run can be found in Supplementary Table~\ref{supp_tab:synthetic_benchmark}.
In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the original scaffolder \npscarf{} was included as well as \npscarfg{} -- its modified version with assembly graph integrated.
On the other hand, \npgraph{} can use 2 different aligners, \bwa{} and \minimap{}, for its bridging phase thus both practices were included in this comparison.

In general, the graph version of \npscarf{} improved the assembly results in terms of mis-assemblies and error reduction while virtually consuming similar resources compared to the original version.
The only exception where the number of mis-assemblies being increased was the simulation of a random sequence with many repeats. There were 10 more mistakes detected using the later version \npscarfg{}. However, with additional investigations, we found that the number of mis-assemblies on the true positive circular sequences (3 from the reference) has been significant reduced by applying assembly graph for \npscarf{}. The errors mostly came from redundant sequences output from the software due to the failure in estimation of contig multiplicity.
Even though using assembly graph for gap fillings, there were no changes in the way \npscarfg{} determine if a contig is unique or not. 
Its implementation still relied on the length and coverage statistics, \IE{} \emph{Astats}~\cite{MyersSD2000} to find anchors that were critical for the backbone construction of the assembly.
Redundant path findings for false positive replicons consequently returned additional wrong translocations in the final contigs which were reported by QUAST. 
Other than that, the method had successfully produced better assemblies than the original. Regarding \emph{Mycobacterium tuberculosis} H37Rv, the number of mis-assembled breakpoints had been trimmed down from 12 to 2, while the number of final contigs had reduced from 4 to only one as in the reference. Results in cases of \ec{} O25b H4ST131 and \emph{Streptococcus suis} BM407 also showed enhancements in terms of those categories as well as N50 statistics. 
There was improvements considering the nucleotide errors (mismatches and indels) as well from aforementioned data sets, except for the \ec{} when slightly more mismatches had been detected. However, these errors can be corrected by running polishing tools with the raw Illumina data afterward.

@@

To align the long reads to the assembly graph components, either \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} was invoked in \npgraph{}. 
The former option was inherited from \npscarf{} pipeline with the intact parameters
%$-k11 -W20 -r10 -A1 -B1 -O1 -E1 -L0 -a -Y$
while the latter was used with the recommended settings (-$\mathtt{k}$15 -$\mathtt{w}$5) for the best sensitivity working on MinION data.
Even though, \bwa{} normally reported more hits than \minimap{} but at the same time, was responsible for more false positive alignments.
For instance, regarding the last data set from Table~\ref{table:npgraph_compare}, the assembly of \npgraph{} using \bwa{} was suffered from the ambiguous alignments thus more fragmented than the other counterparts. 
On the other hand, referring to more complicated graphs from \emph{Acinetobacter} A1 and the yeast \emph{Saccharomyces cerevisiae} S288c from Table~\ref{supp_tab:synthetic_benchmark}, the number of mis-assemblies from using \minimap{} were increased due to the lacks of appropriate alignments to support accurate bridging process.
However, under almost circumstances, using either aligners would result in final assemblies with similar qualities.
Furthermore, in terms of running time and resources required, \minimap{} proved to be the best option. 
The total CPU hours had been cut down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
This feature is certainly more favoured to a real-time assembly as well.
As the consequence, as long as \minimap{} is expected to replace \bwa{} for long-read sequencing data alignment, it would likewise become the main aligner for \npgraph{} pipeline in the future.

To evaluate assembly errors, we considered the measure of the total mismatches and indels per 100kpb from the assembly sequences when mapping to the reference.
As expected from hybrid assembly method embedding Illumina data, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) in almost every cases.
Furthermore, the indels errors, which mainly caused by TGS data, were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
The majority of the differences accounted for the mismatched nucleotides caused by the alternative paths connecting the unique anchors from the backbone of the assembly.
This phenomenon may root from homologous repeats or sequencing errors of the genome.
From all the hybrid assemblers, $\mathtt{hybridSPAdes}$ reported results with highest fidelity. This meant that the performance its decision-rule algorithm $\mathtt{exSPAnder}$~\cite{Prjibelski2014} was the most accurate amongst all path finding methods. As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies in cases of \emph{Streptococcus suis} or \emph{Acinetobacter} samples (Table~\ref{table:npgraph_compare} and \ref{supp_tab:synthetic_benchmark}).
\unicycler{}, which employs an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads, returned the second best reliable and at the same time, closest-to-complete results overall.
\npscarf{}, on the other hand, exploited the long reads for the gap filling thus inherited the high error rates from them.
By integrating the assembly graph for the task, the errors were reduced in general (random sequences, \emph{M.~tuberculosis}, \emph{S.suis} from Table~\ref{table:npgraph_compare}) but not completely since the mis-placed contigs were still not resolved in other circumstances.
\npgraph{} significantly reduced the errors compared to \npscarf{}, however the figures were still higher than the those of the best counterparts.
This implied a more robust decision making system is needed in \npgraph{}'s real-time path finding module for even better output's accuracy.

\subsection*{Hybrid assembly for real data sets}
A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used in this scenario.
The data included both Illumina paired-end reads and MinION sequencing based-call data for each sample.
Due to the unavailability of reference genomes, there were fewer statistics being reported by QUAST for the comparison of the results. 
Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies.
Table~\ref{tab:npgraph_real} shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.

@@

The assembly task for \emph{Enterobacter~cloacae} was observed more challenging as the chromosomal DNA sequence not been fully resolved using either method. 
The chromosome size was estimated to be approximately $4.8$Mbp but had been broken into two smaller pieces. 
\npgraph{} returned longer stretches of length $3.324$Mbp and $1.534$Mbp while the figures were $2.829$Mbp and $1.978$Mbp from \unicycler{}'s output.
However, the number of circular sequences detected by \unicycler{} was one more than the other ($2$ versus $1$). They were corresponding to 2 plasmids, namely IncR and repA.
While the latter were recognized by both methods, the longer plasmid sequence was fragmented running \npgraph{}.
Similar to the previous data set, there were around $14$Kpb of data were unable to be finished by the assemblers.

@@

\subsection*{Assembly performance on streaming data}
Figure~\ref{F:npgraph_rt} demonstrates the real-time mode performance of \npscarf{} and \npgraph{} via N50 statistics during the assembly of 4 example data sets.
This experiment would discover the rate of completing genome assemblies of the new method, set aside the accuracy aspect which had already been discussed previously.
\npscarfg{} basically scaffolds the pre-assembly contigs in the same manner with the original version thus was not discussed here.

@@

\subsection*{Metagenomics assembly on mock community}
We further employed \npgraph{} on mock community data to study the performance of our method in metagenomics co-assembly problem.
In this application, sequencing data (including both short and long reads) from mixtures of ten microbial species of ZymoBIOMICS Microbial Community Standards \cite{Nick2019zymo} were used as input for \npgraph{}. 
The total genome size was estimated as 61.96 Mbp.
There were two settings for the input depending on the distribution of cell abundances in the mixture itself, namely even and log population.
On the other hand, 8 out of 10 genomes being sequenced were reconstructed by using PacBio sequencing (RSII and Sequel) previously \cite{Mcintyre2019zymo}, including \emph{Bacillus~subtills}, \emph{Enterococcus~faecalis}, \emph{Escherichia~coli}, \emph{Listeria~monocytogenes}, \emph{Pseudomonas~aeruginosa}, \emph{Saccharomyces~cerevisiae}, \emph{Salmonella~enterica} and \emph{Staphylococcus~aureus}. We evaluated the coassembly results by running $\mathtt{metaQUAST}$ given 8 PacBio assembly as references.
